\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[margin=0.75in]{geometry}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{fontawesome5} % For icons like Github, Linkedin, Mail
\usepackage{tcolorbox} % For colored boxes
\usepackage{parskip} % Better paragraph spacing
\usepackage{mathptmx} % Use Times/Georgia-like font family
\usepackage[T1]{fontenc} % Better font encoding

% Define colors
\definecolor{linkcolor}{RGB}{25,118,210} % Modern blue
\definecolor{sectioncolor}{RGB}{99,102,241} % Indigo accent
\definecolor{namecolor}{RGB}{15,23,42} % Very dark blue
\definecolor{graytext}{RGB}{71,85,105} % Slate gray
\definecolor{itemcolor}{RGB}{30,41,59} % Dark slate
\definecolor{accentcolor}{RGB}{0,0,0} % 
\definecolor{lightgray}{RGB}{241,245,249} % Light background

% Hyperlink setup
\hypersetup{
    colorlinks=true,
    linkcolor=linkcolor,
    filecolor=magenta,      
    urlcolor=linkcolor,
    citecolor=linkcolor,
}

% Suppress page numbers
\pagenumbering{gobble}

% Set default font family to Times/Georgia-like
\renewcommand{\familydefault}{\rmdefault}

% Section formatting
\titleformat{\section}
  {\Large\bfseries\color{sectioncolor}}
  {\thesection}
  {1em}
  {\color{accentcolor}\rule[-0.3em]{0.5em}{0.4em}\hspace{0.5em}}

\titleformat{\subsection}
  {\large\bfseries\color{sectioncolor}}
  {\thesubsection}
  {1em}
  {}

\titleformat{\subsubsection}
  {\normalsize\bfseries\color{itemcolor}}
  {\thesubsubsection}
  {1em}
  {}

% Reduce spacing between items in lists
\setlist[itemize]{noitemsep, topsep=0.3em, leftmargin=1.5em}
\setlist[enumerate]{noitemsep, topsep=0.3em, leftmargin=1.5em}

% Custom itemize style with colored bullets
\renewcommand{\labelitemi}{\textcolor{accentcolor}{\textbullet}}
\renewcommand{\labelitemii}{\textcolor{accentcolor}{\textendash}}

% Name and Contact Information
\newcommand{\myName}{Jiaqi Shao}
\newcommand{\myInterests}{ LLM Agents \textbar{} MAS \textbar{} Federated Learning \textbar{} Distributed Edge AI}
\newcommand{\myGithub}{https://github.com/SHAO-Jiaqi757} % Replace with actual GitHub link
\newcommand{\myLinkedin}{} % Replace with actual LinkedIn link
\newcommand{\myEmail}{js1139@duke.edu} % Replace with actual email
\newcommand{\myScholar}{https://scholar.google.com/citations?user=P8MtRXMAAAAJ&hl=zh-CN}

\begin{document}

% Header Section
\begin{center}
    {\fontsize{28}{34}\selectfont\textbf{\color{namecolor}\myName}} \\ \vspace{0.3em}
    {\color{graytext}\fontsize{12}{14}\selectfont\myInterests} \\ \vspace{0.4em}
    \begin{tabular}{c c c c}
        \faGithub\enspace \href{\myGithub}{\color{linkcolor}GitHub} &
        \faLinkedin\enspace \href{\myLinkedin}{\color{linkcolor}LinkedIn} &
        \faEnvelope\enspace \href{mailto:\myEmail}{\color{linkcolor}Email} &
        \faGraduationCap\enspace \href{https://scholar.google.com/citations?user=P8MtRXMAAAAJ\&hl=zh-CN}{\color{linkcolor}Google Scholar}
    \end{tabular}
\end{center}
\vspace{0.8em}

% Add a subtle horizontal line
\noindent\color{accentcolor}\rule{\textwidth}{0.5pt}
\vspace{0.8em}

% Navigation (Optional in PDF, more for web - but can be kept for structure)
% \begin{center}
%     \href{#education}{\color{graytext}Education} \quad \textbar \quad
%     \href{#publications}{\color{graytext}Publications} \quad \textbar \quad
%     \href{#projects}{\color{graytext}Projects} \quad \textbar \quad
%     \href{#teaching}{\color{graytext}Teaching} \quad \textbar \quad
%     \href{#about}{\color{graytext}About}
% \end{center}
% \vspace{1em}


% Education Section
\section*{\color{sectioncolor}Education}
    \subsubsection*{\color{itemcolor}Hong Kong University of Science and Technology}
    \textit{\color{graytext}Doctor of Philosophy (PhD) in Electronic and Computer Engineering} \hfill \color{accentcolor}\textbf{2023 Fall – Present} \\
    \begin{itemize}[leftmargin=*, label=\textcolor{accentcolor}{\textbullet}]
        \vspace{-1em}
        \item \small{\color{graytext}Supervisor: Prof. Wei Zhang (HKUST) (Mentor: Prof. Bing Luo (DKU))}
    \end{itemize}
    \vspace{0.3em}
    \subsubsection*{\color{itemcolor}The Chinese University of Hong Kong, Shenzhen}
    \textit{\color{graytext}Bachelor of Engineering in Electrical and Computer Engineer} \hfill \color{accentcolor}\textbf{2019 – 2023} \\
    \begin{itemize}[leftmargin=*, label=\textcolor{accentcolor}{\textbullet}]
        \vspace{-1em}
        \item \small{\color{graytext}Stream: Computer Engineering}
    \end{itemize}
\vspace{0.8em}

% Publications Section
\section*{\color{sectioncolor}Publications}
\begin{enumerate}[label=\textcolor{accentcolor}{\arabic*.}, leftmargin=*, itemsep=0.6em]
    \item \textbf{Shao, J.}, Lin, Y., Lohani, M. P., Miao, Y., and Luo, B., "Do LLM Agents Know How to Ground, Recover, and Assess? A Benchmark for Epistemic Competence in Information-Seeking Agents", \textit{arXiv e-prints}, arXiv:2509.22391, 2025.
    \item \textbf{Shao, J.}, Lin, T., Luo, B., "Beyond Right to be Forgotten: Managing Heterogeneity Side Effects Through Strategic Incentives", \textit{ACM MobiHoc}, 2025.
    \item Fan, T., ..., \textbf{Shao, J.}, et al., "Ten challenging problems in federated foundation models", \textit{IEEE Transactions on Knowledge and Data Engineering}, 2025.
    \item Lu, S., \textbf{Shao, J.}$^{*}$, Luo, B., and Lin, T., "Morphagent: Empowering agents through self-evolving profiles and decentralized collaboration", \textit{ICML-MAS}, 2025. ($^{*}$Co-first authors.)
    \item \textbf{Shao, J.}, Yuan, T., Lin, T., and Luo, B., "Cognitive Insights and Stable Coalition Matching for Fostering Multi-Agent Cooperation," \textit{arXiv preprint arXiv:2405.18044}, 2024.
    \item \textbf{Shao, J.}, Lin, T., and Luo, B., "Federated Unlearning: a Perspective of Stability and Fairness", \textit{arXiv preprint arXiv:2402.01276}, 2024.
    \item He, S., Tang, B., Zhang, B., \textbf{Shao, J.}, Ouyang, X., Nugraha, DN., Luo, B., "FedKit: Enabling Cross-Platform Federated Learning for Android and iOS", \textit{IEEE INFOCOM 2024-IEEE Conference on Computer Communications Workshops}, 2024.
    \item Geng, J., Tang, B., Zhang, B., \textbf{Shao, J.}, Luo, B., "FedCampus: A Real-world Privacy-preserving Mobile Application for Smart Campus via Federated Learning \& Analytics", \textit{Proceedings of the Twenty-Fifth International Symposium on Theory}, 2024.


\end{enumerate}
\vspace{0.5em}

% Projects Section
\section*{\color{sectioncolor}Projects}
    \subsubsection*{\color{itemcolor}MASArena: Benchmarking Framework for Multi-Agent Systems}
    \begin{itemize}[leftmargin=*, label=\textcolor{accentcolor}{\textbullet}]
        \item Led the design and implementation of the overall architecture for an open-source, modular benchmarking framework for single- and multi-agent systems.
        \item Collaborated with Westlake University LINs-Lab to develop plug-and-play modules, built-in benchmarks, visual debugging, and easy agent/tool/dataset integration.
        \item Designed framework to support academic experiment reproduction, agent comparison, and toolchain evaluation.
        \item Open-source and actively maintained. Available at: \href{https://github.com/LINs-lab/MASArena}{\color{linkcolor}https://github.com/LINs-lab/MASArena}
    \end{itemize}
    \vspace{0.6em}
    \subsubsection*{\color{itemcolor}FedKit: Enabling Cross-Platform Federated Learning for Android and iOS}
    \begin{itemize}[leftmargin=*, label=\textcolor{accentcolor}{\textbullet}]
        \item Developed FEDKIT, which pipelines Cross-Platform FL for Android and iOS development by enabling model conversion, hardware-accelerated training, and cross-platform model aggregation.
        \item Implemented workflow supporting flexible federated learning operations (FLOps) in production, facilitating continuous model delivery and training.
        \item Collaborated with Prof. Luo, DKU undergraduate students Sichang He (lead), Beilong Tang, and Boyan Zhang, as well as collaborators Xiaomin Ouyang (UCLA) and Daniel Nata (Flower).
        \item Work accepted at IEEE INFOCOM 2024 Demo.
    \end{itemize}
    \vspace{0.6em}
    \subsubsection*{\color{itemcolor}FedCampus: Privacy-preserving Mobile Application for Smart Campus}
    \begin{itemize}[leftmargin=*, label=\textcolor{accentcolor}{\textbullet}]
        \item Designed and implemented a real-world mobile application leveraging federated learning and differential privacy for smart campus services.
        \item Deployed 100 customized smart watches for participants at DKU and developed FedCampus APP for Android and iOS.
        \item Integrated privacy-preserving analytics to enable data-driven campus improvements without compromising individual user data.
        \item Video demonstration available online showcasing the application's capabilities.
    \end{itemize}
    \vspace{0.6em}
    \subsubsection*{\color{itemcolor}Edge-based Cross-device Federated Learning Prototypes}
    \begin{itemize}[leftmargin=*, label=\textcolor{accentcolor}{\textbullet}]
        \item Developed prototypes supporting Mobile and IoT devices operating at WiFi and USRP-based 4G/5G wireless networks.
        \item Collaborated with Prof. Luo and students from CUHKSZ to implement cross-device federated learning solutions.
        \item Focused on edge computing and distributed machine learning in heterogeneous network environments.
    \end{itemize}
\vspace{0.8em}

% Teaching Section
\section*{\color{sectioncolor}Teaching}
    \subsubsection*{\color{itemcolor}Teaching Assistant}
    \begin{itemize}[leftmargin=*, label=\textcolor{accentcolor}{\textbullet}]
        \item ELEC3120: Computer Communication Networks (HKUST, Spring 2024)
        \item ELEC3300: Introduction to Embedded Systems (HKUST, Fall 2024)
        \item Vector Space Methods with Applications | ECE 586K (DKU, Spring 2025)
    \end{itemize}
\vspace{0.8em}

% Patents Section
\section*{\color{sectioncolor}Patents}
\begin{itemize}[leftmargin=*, label=\textcolor{accentcolor}{\textbullet}, itemsep=0.4em]
    \item B. Luo, \textbf{J. Shao}, Method and Apparatus for Online Parameter Selection in Minimizing the Total Cost of Federated Learning, CN202310485067.8, Apr. 2023, filed
    \item B. Luo, \textbf{J. Shao}, Method and Apparatus for Online Client Sampling in Minimizing the Training time of Federated Learning, CN 202310484383.3, Apr. 2023, filed
    \item B. Luo, \textbf{J. Shao}, J. Huang, Method and Apparatus for Frequent Items Mining Using Federated Analytics, CN202310365167.7, Mar. 2023, filed
    \item B. Luo, \textbf{J. Shao}, J. Huang, Method and Apparatus for Frequent Data Mining Based on Hierarchical Federated Analytics, CN202310330791.3, Mar. 2023, filed
\end{itemize}
\vspace{0.8em}

% % About Section
% \section*{\color{sectioncolor}About}
% \begin{flushleft}
%     \color{graytext}
%     I am a PhD student at the Hong Kong University of Science and Technology (HKUST), where I work on federated learning, distributed edge AI, and privacy-preserving machine learning. My research focuses on developing efficient and privacy-preserving algorithms for distributed machine learning systems.

%     Prior to joining HKUST, I completed my bachelor's degree at The Chinese University of Hong Kong, Shenzhen, where I specialized in Computer Engineering. During my undergraduate studies, I developed a strong interest in machine learning and distributed systems.
% \end{flushleft}
% \vspace{1em}



\end{document}